---
title: "Redlining Analysis: CES Pollution Burden - Environmental Effects"
# author: "David"
date: "*Updated: `r format(Sys.Date())`*"
# output: html_document
output:
  html_document:
    code_folding: hide
    toc: TRUE
    toc_float: TRUE
    toc_depth: 5
---

```{r setup, include=FALSE, echo=FALSE}
    knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, error = FALSE)
    options(scipen = 999)
```

```{r packages}
    # Markdown
        # library(bookdown)
    # General data analysis and transformation
        library(readr)
        library(readxl)
        library(dplyr)
        library(janitor)
        # library(gtools)
        library(stringr)
        library(units)
        library(tidyr)
        library(rlang)
    # API-related
        # library(jsonlite)
        # library(urltools)
    # Mapping and GIS operations
        library(sf)
        # library(leaflet)
        # library(htmlwidgets)
        # library(geojsonsf)
        # library(rmapshaper)
        library(tmap)
        library(tmaptools)
        library(ceramic)
    # workflow
        library(here)
    # plotting
        library(ggplot2)
        library(forcats)
```

```{r ces measures list}
# Get list of CES 3 variable names and plain text names
    ces3_variables <- readr::read_csv(here('data_processed', 'ces_names.csv'))

ces_measures_effects <- ces3_variables %>% 
    filter(group == 'pollution burden', 
           subgroup == 'environmental effects', 
           type == 'percentile')

ces_measures_exposures <- ces3_variables %>% 
    filter(group == 'pollution burden', 
           subgroup == 'exposures', 
           type == 'percentile')

ces_measures_sensitive_pops <- ces3_variables %>% 
    filter(group == 'population characteristics', 
           subgroup == 'sensitive populations', 
           type == 'percentile')

ces_measures_socioeconomic <- ces3_variables %>% 
    filter(group == 'population characteristics', 
           subgroup == 'socioeconomic factors', 
           type == 'percentile')

```

## Introduction
This document attempts to do some quantitative geospatial analysis to look at correlations between redline mapping and indicators of water quality, public health, and facility information. It computes the area weighed average percentile for different CalEnviroScreen 3.0 (CES) indicators by HOLC rating for a given city and statewide. CES considers two broad categories of indicators, (1) Pollution Burden and (2) Population Characteristics, which are both further broken down into two sub-categories each ([factsheet](https://oehha.ca.gov/media/downloads/calenviroscreen/fact-sheet/ces30factsheetfinal.pdf), [indicators page](https://oehha.ca.gov/calenviroscreen/indicators)).

The Pollution Burden category includes the following indicators:

- Environmental Effects
    + `r ces_measures_effects$name[1]`
    + `r ces_measures_effects$name[2]`
    + `r ces_measures_effects$name[3]`
    + `r ces_measures_effects$name[4]`
    + `r ces_measures_effects$name[5]`
- Exposures
    + `r ces_measures_exposures$name[1]`
    + `r ces_measures_exposures$name[2]`
    + `r ces_measures_exposures$name[3]`
    + `r ces_measures_exposures$name[4]`
    + `r ces_measures_exposures$name[5]`
    + `r ces_measures_exposures$name[6]`
    + `r ces_measures_exposures$name[7]`

The Population Characteristics category includes the following indicators:

- Sensitive Populations
    + `r ces_measures_sensitive_pops$name[1]`
    + `r ces_measures_sensitive_pops$name[2]`
    + `r ces_measures_sensitive_pops$name[3]`
- Socioeconomic Factors
    + `r ces_measures_socioeconomic$name[1]`
    + `r ces_measures_socioeconomic$name[2]`
    + `r ces_measures_socioeconomic$name[3]`
    + `r ces_measures_socioeconomic$name[4]`
    + `r ces_measures_socioeconomic$name[5]`


### Analysis Notes
  
The CES polygons and the Redline polygons have different coverages, as shown in the maps below. In the first map for each indicator, the left pane of each map shows the HOLC rated areas, the center pane shows the CES indicator scores (at the census tract level) with the Redlined areas superimposed on top, and the right pane shows the overlapping portions of the CES polygons and the redlined areas (border colors represent HOLC rating).


```{r load data}
    # load data
        # Redline Polygons
            redline_polygons <- read_rds(here('data_processed', 'redline_polygons.gpkg'))
                # st_crs(redline_polygons) # to check the reference system
            # modify the 'city' column to better keep track when joining with other datasets
                redline_polygons <- redline_polygons %>% rename('redline_city' = 'city')
            # add the area of each redline polygon
                redline_polygons <- redline_polygons %>% mutate(redline_poly_area = st_area(.))
                
    # NOTE: not all redline polygons have an HOLC ID listed - create a unique ID for each one with a missing ID (so that each unique HOLC polygon can be associated with a weighted average CES score)
    # create new column for the new holc id to be assigned
        redline_polygons <- redline_polygons %>% 
            mutate('holc_id_2' = holc_id) %>% 
            arrange(redline_city, holc_grade, holc_id)
    # initialiaze some variables for the loop below
        grade_city_vec <- c()
        j <- 1
    # loop through all HOLC polygons ...
        for (i_row in 1:nrow(redline_polygons)) {
            cur_id <- redline_polygons$holc_id[i_row]
            grade <- redline_polygons$holc_grade[i_row]
            city <- redline_polygons$redline_city[i_row] 
            # the current combination of grade and city
                grade_city_cur <- paste0(city, '_', grade)
            # if the holc id is NA, check to see if there are already other missing holc id's for that city/grade combination - if so, increment a counter by 1, otherwise set counter (back) to 1
                if (is.na(cur_id)) {
                    if(grade_city_cur %in%  grade_city_vec) {
                        grade_city_counter <- grade_city_counter + 1
                    } else {
                        grade_city_counter <- 1
                    }
            # enter a new unique ID for the row with the missing ID
                redline_polygons$holc_id_2[i_row] <- paste0('unknown_', 
                                                            grade, '_', 
                                                            grade_city_counter)
            # add the grade/city combo to a running list to track number of missing holc id's for that city/grade combination
                grade_city_vec[j] <- grade_city_cur
                j <- j + 1
            }
    
    }
    
        # CES 3 Polygons
            ces_3_poly <- read_sf(here('data_raw', 'CalEnviroScreen3', 'CESJune2018Update_SHP','CES3June2018Update.shp'))
                # st_crs(ces_3_poly) # to check the reference system
            # modify the 'City' column to better keep track when joining with other datasets
                ces_3_poly <- ces_3_poly %>% rename('CES_City' = 'City')
                
        # Transform both to UTM Zone 10N
            redline_polygons <- redline_polygons %>% st_transform(crs = 26910)
            ces_3_poly <- ces_3_poly %>% st_transform(crs = 26910)
            
    # create a map to check that the data loaded correctly
        # tm_shape(ces_3_poly) + tm_borders() + tm_shape(redline_polygons) + tm_borders(col = 'red')
            
```



```{r basemap-background}
    # get a basemap (See: https://github.com/mtennekes/tmap/issues/185)
        Sys.setenv(MAPBOX_API_KEY = "pk.eyJ1IjoiZGFsdGFyZSIsImEiOiJjazZqcm5ocHgwMG84M2tteGc5eWd4YXNmIn0.nHiYenoq-wFWwH3V4vtPXA")
        background <- cc_location(ces_3_poly %>% filter(CES_City == 'Sacramento'), verbose = FALSE)
```


```{r map-redline}
    # create map
        map_redline <- tm_shape(background) + 
            tm_rgb(alpha = 0.5) + 
            tm_shape(redline_polygons %>% filter(redline_city == 'Sacramento'), is.master = TRUE) + 
            tm_polygons('holc_grade', palette = c('green', 'blue', 'yellow', 'red'), title = 'HOLC Grade') + 
            tm_layout(legend.bg.color = 'white', legend.bg.alpha = 0.7, legend.frame = TRUE)
```



```{r ces3-redline intersection}
    # get the intersection of the CES polygons and redline polygons
        ces3_redline_intersection <- st_intersection(ces_3_poly, redline_polygons)
    # inspect
        # glimpse(ces3_redline_intersection)

# add the area of each clipped polygon to the data frame
        ces3_redline_intersection <- ces3_redline_intersection %>% 
          mutate(clipped_area = st_area(.))
            # glimpse(ces3_redline_intersection)
# # write to output file 
    # st_write(obj = ces3_redline_intersection,
    #          here('analysis-output', 'ces3_redline_intersection.shp'))
```


```{r ces polygon map Function}
    ces_poly_map <- function(ces_id, ces_measure_name) {
        # plot the CES polygons
        map_ces <- tm_shape(background) + 
            tm_rgb(alpha = 0.5) + 
            tm_shape(ces_3_poly %>% filter(CES_City == 'Sacramento' | CES_City == 'West Sacramento')) + 
            tm_polygons(col = ces_id, title = ces_measure_name, border.alpha = 1) + 
            tm_shape(ces3_redline_intersection %>% filter(redline_city == 'Sacramento'), is.master = TRUE) +
            tm_borders(lwd = 0, alpha = 0) +
            # tm_shape(redline_polygons %>% filter(redline_city == 'Sacramento')) +
            # tm_borders(lwd = 2, col = 'black') +
            tm_shape(redline_polygons %>% 
                       filter(redline_city == 'Sacramento', holc_grade == 'D')) + 
            tm_borders(lwd = 2, col = 'red') + 
            tm_shape(redline_polygons %>% 
                       filter(redline_city == 'Sacramento', holc_grade == 'C')) + 
            tm_borders(lwd = 2, col = 'gold2') + 
            tm_shape(redline_polygons %>% 
                       filter(redline_city == 'Sacramento', holc_grade == 'B')) + 
            tm_borders(lwd = 2, col = 'blue') + 
            tm_shape(redline_polygons %>% 
                       filter(redline_city == 'Sacramento', holc_grade == 'A')) + 
            tm_borders(lwd = 2, col = 'green') +
            # tm_text('holc_grade', size = 0.5) + 
            tm_layout(legend.bg.color = 'white', legend.bg.alpha = 0.7, legend.frame = TRUE)
        map_ces
        
    }
```


```{r CES-Redline Overlap Map Function}
    ces_redline_overlap_map <- function(ces_id, ces_measure_name) {
        map_overlap <- tm_shape(background) + 
            tm_rgb(alpha = 0.5) + 
            tm_shape(ces_3_poly %>% filter(CES_City == 'Sacramento')) + 
            tm_borders(lwd = 1) + 
            tm_shape(ces3_redline_intersection %>% filter(redline_city == 'Sacramento'), is.master = TRUE) + 
            tm_polygons(col = ces_id, title = ces_measure_name, border.alpha = 0) + 
            # tm_shape(redline_polygons %>% filter(redline_city == 'Sacramento')) + 
            # tm_borders(lwd = 2, col = 'black') + 
            tm_shape(redline_polygons %>% 
                       filter(redline_city == 'Sacramento', holc_grade == 'D')) + 
            tm_borders(lwd = 2, col = 'red') + 
            tm_shape(redline_polygons %>% 
                       filter(redline_city == 'Sacramento', holc_grade == 'C')) + 
            tm_borders(lwd = 2, col = 'gold2') + 
            tm_shape(redline_polygons %>% 
                       filter(redline_city == 'Sacramento', holc_grade == 'B')) + 
            tm_borders(lwd = 2, col = 'blue') + 
            tm_shape(redline_polygons %>% 
                       filter(redline_city == 'Sacramento', holc_grade == 'A')) + 
            tm_borders(lwd = 2, col = 'green') + 
            #tm_text('holc_grade', size = 0.5) + 
            tm_layout(legend.bg.color = 'white', legend.bg.alpha = 0.7, legend.frame = TRUE)
        map_overlap
    }
```


```{r Facet Map Function}
    # FACET MAP
    ces_redline_facet_map <- function(ces_id, ces_measure_name) {
        map_facets <- tm_shape(ces_3_poly %>% filter(CES_City == 'Sacramento')) +
            tm_borders(lwd = 1) +
            tm_shape(background) +
            tm_rgb(alpha = 0.5) +
            tm_shape(ces3_redline_intersection %>% 
                         filter(redline_city == 'Sacramento'), is.master = TRUE) +
            # tm_shape(ces3_redline_intersection %>% filter(redline_city == 'Sacramento')) +
            tm_facets(by = 'holc_grade', free.coords = FALSE) +
            tm_polygons(col = ces_id, title = ces_measure_name, border.alpha = 0) +
            tm_shape(redline_polygons %>% filter(redline_city == 'Sacramento')) + 
            tm_facets(by = 'holc_grade') +
            tm_borders(lwd = 2, col = 'black')  +
            # # D
            # tm_shape(redline_polygons %>%
            #            filter(redline_city == 'Sacramento', holc_grade == 'D')) +
            # tm_facets(by = 'holc_grade') +
            # tm_borders(lwd = 2, col = 'red') +
            # # C
            # tm_shape(redline_polygons %>% 
            #            filter(redline_city == 'Sacramento', holc_grade == 'C')) + 
            # tm_borders(lwd = 2, col = 'gold2') + 
            # tm_facets(by = 'holc_grade') +
            # # B
            # tm_shape(redline_polygons %>% 
            #            filter(redline_city == 'Sacramento', holc_grade == 'B')) + 
            # tm_borders(lwd = 2, col = 'blue') + 
            # tm_facets(by = 'holc_grade') +
            # # A
            # tm_shape(redline_polygons %>% 
            #            filter(redline_city == 'Sacramento', holc_grade == 'A')) + 
            # tm_borders(lwd = 2, col = 'green') + 
            # tm_facets(by = 'holc_grade') +
            #
            tm_legend(bg.color= 'white', frame = TRUE)

        map_facets
    }
```


```{r bar plot function - city plus statewide}
ces_scores_plot <- function(ces_id, ces_measure_name) {
    
    # group by city and holc rating, then compute the weighted average score for each
        ces3_redline_grouped <- ces3_redline_intersection %>% 
            st_drop_geometry() %>%
            mutate(area_x_score = clipped_area * (!!as.name(ces_id))) %>% 
            group_by(redline_city, holc_grade) %>% 
            summarize(total_area = sum(clipped_area), 
                      area_x_score_total = sum(area_x_score)) %>% 
            mutate(weighted_score = area_x_score_total / total_area) %>% 
            drop_units()

    ces3_redline_grouped_statewide <- ces3_redline_grouped %>%
            group_by(holc_grade) %>%
            summarize(total_area = sum(total_area),
                      area_x_score_total = sum(area_x_score_total)) %>%
            mutate(weighted_score = area_x_score_total / total_area) %>%
            mutate(redline_city = '**Statewide**') %>%
            drop_units()

    ces3_redline_grouped_city_state <- bind_rows(ces3_redline_grouped, ces3_redline_grouped_statewide)

    # plot the results by city and holc rating, and include statewide summary
        g_city_state <- ggplot(ces3_redline_grouped_city_state) +
            aes(x = fct_relevel(fct_reorder(redline_city, weighted_score), 
                                c('**Statewide**'), 
                                after = 0), 
                y = weighted_score, 
                fill = fct_rev(holc_grade)) +
            geom_bar(stat = 'identity', position = 'dodge') +
            geom_vline(xintercept = 1.52, size = 0.5, color = 'grey50') +
            scale_fill_manual(values = rev(c('green', 'blue', 'yellow', 'red'))) +
            guides(fill = guide_legend(reverse = TRUE)) +
            labs(fill = 'HOLC Rating', 
                 title = ces_measure_name,
                 x = NULL, 
                 y = "Area Weighted Average Score By City") +
            coord_flip()

        g_city_state
}
```



## Pollution Burden - Environmental Effects

### `r ces_measures_effects$name[1]`
```{r ces indicator EF 1}
    i_map <- 1
    ces_measure_name <- ces_measures_effects$name[i_map]
    ces_id <- ces_measures_effects$id[i_map]
    
    map_ces <- ces_poly_map(ces_id, ces_measure_name)
    map_overlap <- ces_redline_overlap_map(ces_id, ces_measure_name)
    
    tmap_arrange(map_redline, map_ces, map_overlap, nrow = 1)
    
    ces_redline_facet_map(ces_id, ces_measure_name)
    
    ces_scores_plot(ces_id, ces_measure_name)
```

### `r ces_measures_effects$name[2]`
```{r ces indicator EF 2}
    i_map <- 2
    ces_measure_name <- ces_measures_effects$name[i_map]
    ces_id <- ces_measures_effects$id[i_map]
    
    map_ces <- ces_poly_map(ces_id, ces_measure_name)
    map_overlap <- ces_redline_overlap_map(ces_id, ces_measure_name)
    
    tmap_arrange(map_redline, map_ces, map_overlap, nrow = 1)
    
    ces_redline_facet_map(ces_id, ces_measure_name)
    
    ces_scores_plot(ces_id, ces_measure_name)
```


### `r ces_measures_effects$name[3]`
```{r ces indicator EF 3}
    i_map <- 3
    ces_measure_name <- ces_measures_effects$name[i_map]
    ces_id <- ces_measures_effects$id[i_map]
    
    map_ces <- ces_poly_map(ces_id, ces_measure_name)
    map_overlap <- ces_redline_overlap_map(ces_id, ces_measure_name)
    
    tmap_arrange(map_redline, map_ces, map_overlap, nrow = 1)
    
    ces_redline_facet_map(ces_id, ces_measure_name)
    
    ces_scores_plot(ces_id, ces_measure_name)
```


### `r ces_measures_effects$name[4]`
```{r ces indicator EF 4}
    i_map <- 4
    ces_measure_name <- ces_measures_effects$name[i_map]
    ces_id <- ces_measures_effects$id[i_map]
    
    map_ces <- ces_poly_map(ces_id, ces_measure_name)
    map_overlap <- ces_redline_overlap_map(ces_id, ces_measure_name)
    
    tmap_arrange(map_redline, map_ces, map_overlap, nrow = 1)
    
    ces_redline_facet_map(ces_id, ces_measure_name)
    
    ces_scores_plot(ces_id, ces_measure_name)
```


### `r ces_measures_effects$name[5]`
```{r ces indicator EF 5}
    i_map <- 5
    ces_measure_name <- ces_measures_effects$name[i_map]
    ces_id <- ces_measures_effects$id[i_map]
    
    map_ces <- ces_poly_map(ces_id, ces_measure_name)
    map_overlap <- ces_redline_overlap_map(ces_id, ces_measure_name)
    
    tmap_arrange(map_redline, map_ces, map_overlap, nrow = 1)
    
    ces_redline_facet_map(ces_id, ces_measure_name)
    
    ces_scores_plot(ces_id, ces_measure_name)
```


## Pollution Burden - Exposures

### `r ces_measures_exposures$name[1]`
```{r ces indicator EX 1}
    i_map <- 1
    ces_measure_name <- ces_measures_exposures$name[i_map]
    ces_id <- ces_measures_exposures$id[i_map]
    
    map_ces <- ces_poly_map(ces_id, ces_measure_name)
    map_overlap <- ces_redline_overlap_map(ces_id, ces_measure_name)
    
    tmap_arrange(map_redline, map_ces, map_overlap, nrow = 1)
    
    ces_redline_facet_map(ces_id, ces_measure_name)
    
    ces_scores_plot(ces_id, ces_measure_name)
```

### `r ces_measures_exposures$name[2]`
```{r ces indicator EX 2}
    i_map <- 2
    ces_measure_name <- ces_measures_exposures$name[i_map]
    ces_id <- ces_measures_exposures$id[i_map]
    
    map_ces <- ces_poly_map(ces_id, ces_measure_name)
    map_overlap <- ces_redline_overlap_map(ces_id, ces_measure_name)
    
    tmap_arrange(map_redline, map_ces, map_overlap, nrow = 1)
    
    ces_redline_facet_map(ces_id, ces_measure_name)
    
    ces_scores_plot(ces_id, ces_measure_name)
```


### `r ces_measures_exposures$name[3]`
```{r ces indicator EX 3}
    i_map <- 3
    ces_measure_name <- ces_measures_exposures$name[i_map]
    ces_id <- ces_measures_exposures$id[i_map]
    
    map_ces <- ces_poly_map(ces_id, ces_measure_name)
    map_overlap <- ces_redline_overlap_map(ces_id, ces_measure_name)
    
    tmap_arrange(map_redline, map_ces, map_overlap, nrow = 1)
    
    ces_redline_facet_map(ces_id, ces_measure_name)
    
    ces_scores_plot(ces_id, ces_measure_name)
```


### `r ces_measures_exposures$name[4]`
```{r ces indicator EX 4}
    i_map <- 4
    ces_measure_name <- ces_measures_exposures$name[i_map]
    ces_id <- ces_measures_exposures$id[i_map]
    
    map_ces <- ces_poly_map(ces_id, ces_measure_name)
    map_overlap <- ces_redline_overlap_map(ces_id, ces_measure_name)
    
    tmap_arrange(map_redline, map_ces, map_overlap, nrow = 1)
    
    ces_redline_facet_map(ces_id, ces_measure_name)
    
    ces_scores_plot(ces_id, ces_measure_name)
```


### `r ces_measures_exposures$name[5]`
```{r ces indicator EX 5}
    i_map <- 5
    ces_measure_name <- ces_measures_exposures$name[i_map]
    ces_id <- ces_measures_exposures$id[i_map]
    
    map_ces <- ces_poly_map(ces_id, ces_measure_name)
    map_overlap <- ces_redline_overlap_map(ces_id, ces_measure_name)
    
    tmap_arrange(map_redline, map_ces, map_overlap, nrow = 1)
    
    ces_redline_facet_map(ces_id, ces_measure_name)
    
    ces_scores_plot(ces_id, ces_measure_name)
```


### `r ces_measures_exposures$name[6]`
```{r ces indicator EX 6}
    i_map <- 6
    ces_measure_name <- ces_measures_exposures$name[i_map]
    ces_id <- ces_measures_exposures$id[i_map]
    
    map_ces <- ces_poly_map(ces_id, ces_measure_name)
    map_overlap <- ces_redline_overlap_map(ces_id, ces_measure_name)
    
    tmap_arrange(map_redline, map_ces, map_overlap, nrow = 1)
    
    ces_redline_facet_map(ces_id, ces_measure_name)
    
    ces_scores_plot(ces_id, ces_measure_name)
```


### `r ces_measures_exposures$name[7]`
```{r ces indicator EX 7}
    i_map <- 7
    ces_measure_name <- ces_measures_exposures$name[i_map]
    ces_id <- ces_measures_exposures$id[i_map]
    
    map_ces <- ces_poly_map(ces_id, ces_measure_name)
    map_overlap <- ces_redline_overlap_map(ces_id, ces_measure_name)
    
    tmap_arrange(map_redline, map_ces, map_overlap, nrow = 1)
    
    ces_redline_facet_map(ces_id, ces_measure_name)
    
    ces_scores_plot(ces_id, ces_measure_name)
```


## Population Characteristics - Sensitive Populations

### `r ces_measures_sensitive_pops$name[1]`
```{r ces indicator SP 1}
    i_map <- 1
    ces_measure_name <- ces_measures_sensitive_pops$name[i_map]
    ces_id <- ces_measures_sensitive_pops$id[i_map]
    
    map_ces <- ces_poly_map(ces_id, ces_measure_name)
    map_overlap <- ces_redline_overlap_map(ces_id, ces_measure_name)
    
    tmap_arrange(map_redline, map_ces, map_overlap, nrow = 1)
    
    ces_redline_facet_map(ces_id, ces_measure_name)
    
    ces_scores_plot(ces_id, ces_measure_name)
```


### `r ces_measures_sensitive_pops$name[2]`
```{r ces indicator SP 2}
    i_map <- 2
    ces_measure_name <- ces_measures_sensitive_pops$name[i_map]
    ces_id <- ces_measures_sensitive_pops$id[i_map]
    
    map_ces <- ces_poly_map(ces_id, ces_measure_name)
    map_overlap <- ces_redline_overlap_map(ces_id, ces_measure_name)
    
    tmap_arrange(map_redline, map_ces, map_overlap, nrow = 1)
    
    ces_redline_facet_map(ces_id, ces_measure_name)
    
    ces_scores_plot(ces_id, ces_measure_name)
```


### `r ces_measures_sensitive_pops$name[3]`
```{r ces indicator SP 3}
    i_map <- 3
    ces_measure_name <- ces_measures_sensitive_pops$name[i_map]
    ces_id <- ces_measures_sensitive_pops$id[i_map]
    
    map_ces <- ces_poly_map(ces_id, ces_measure_name)
    map_overlap <- ces_redline_overlap_map(ces_id, ces_measure_name)
    
    tmap_arrange(map_redline, map_ces, map_overlap, nrow = 1)
    
    ces_redline_facet_map(ces_id, ces_measure_name)
    
    ces_scores_plot(ces_id, ces_measure_name)
```



## Population Characteristics - Socioeconomic Factors

### `r ces_measures_socioeconomic$name[1]`
```{r ces indicator SE 1}
    i_map <- 1
    ces_measure_name <- ces_measures_socioeconomic$name[i_map]
    ces_id <- ces_measures_socioeconomic$id[i_map]
    
    map_ces <- ces_poly_map(ces_id, ces_measure_name)
    map_overlap <- ces_redline_overlap_map(ces_id, ces_measure_name)
    
    tmap_arrange(map_redline, map_ces, map_overlap, nrow = 1)
    
    ces_redline_facet_map(ces_id, ces_measure_name)
    
    ces_scores_plot(ces_id, ces_measure_name)
```


### `r ces_measures_socioeconomic$name[2]`
```{r ces indicator SE 2}
    i_map <- 2
    ces_measure_name <- ces_measures_socioeconomic$name[i_map]
    ces_id <- ces_measures_socioeconomic$id[i_map]
    
    map_ces <- ces_poly_map(ces_id, ces_measure_name)
    map_overlap <- ces_redline_overlap_map(ces_id, ces_measure_name)
    
    tmap_arrange(map_redline, map_ces, map_overlap, nrow = 1)
    
    ces_redline_facet_map(ces_id, ces_measure_name)
    
    ces_scores_plot(ces_id, ces_measure_name)
```


### `r ces_measures_socioeconomic$name[3]`
```{r ces indicator SE 3}
    i_map <- 3
    ces_measure_name <- ces_measures_socioeconomic$name[i_map]
    ces_id <- ces_measures_socioeconomic$id[i_map]
    
    map_ces <- ces_poly_map(ces_id, ces_measure_name)
    map_overlap <- ces_redline_overlap_map(ces_id, ces_measure_name)
    
    tmap_arrange(map_redline, map_ces, map_overlap, nrow = 1)
    
    ces_redline_facet_map(ces_id, ces_measure_name)
    
    ces_scores_plot(ces_id, ces_measure_name)
```


### `r ces_measures_socioeconomic$name[4]`
```{r ces indicator SE 4}
    i_map <- 4
    ces_measure_name <- ces_measures_socioeconomic$name[i_map]
    ces_id <- ces_measures_socioeconomic$id[i_map]
    
    map_ces <- ces_poly_map(ces_id, ces_measure_name)
    map_overlap <- ces_redline_overlap_map(ces_id, ces_measure_name)
    
    tmap_arrange(map_redline, map_ces, map_overlap, nrow = 1)
    
    ces_redline_facet_map(ces_id, ces_measure_name)
    
    ces_scores_plot(ces_id, ces_measure_name)
```


### `r ces_measures_socioeconomic$name[5]`
```{r ces indicator SE 5}
    i_map <- 5
    ces_measure_name <- ces_measures_socioeconomic$name[i_map]
    ces_id <- ces_measures_socioeconomic$id[i_map]
    
    map_ces <- ces_poly_map(ces_id, ces_measure_name)
    map_overlap <- ces_redline_overlap_map(ces_id, ces_measure_name)
    
    tmap_arrange(map_redline, map_ces, map_overlap, nrow = 1)
    
    ces_redline_facet_map(ces_id, ces_measure_name)
    
    ces_scores_plot(ces_id, ces_measure_name)
```


## Create Output Shapefile
The code below creates a shapefile with the calculated weighted average scores for all HOLC polygons across all of the CES indicators. 

Note that the field names are the same as those used in the original CES shapefile, but in the output shapefile produced by the code below the values refer to the calculated weighted average scores. 

Also, note that this output shapefile contains a field called 'holc_id_2' rather than 'holc_id'. This 'holc_id_2' is a revised version of the 'holc_id_field' - this is needed because not all HOLC polygons are labeled with an HOLC ID in the source shapefiles (from the University of Richmond site), so it was necessary to create a unique HOLC ID within each city/grade combination so that the clipped CES polygons could all be grouped to a unique HOLC polygon. In the 'holc_id_2' field, those records with missing HOLC IDs have an entry with the format "unknown_X_Y", where X is the HOLC grade and Y is a number. 

```{r create output shapefile for each holc polygon}
ces_measures_combined <- bind_rows(ces_measures_effects, 
                                   ces_measures_exposures, 
                                   ces_measures_sensitive_pops, 
                                   ces_measures_socioeconomic)

for (i_output in seq(nrow(ces_measures_combined))) {
    ces_measure_name <- ces_measures_combined$name[i_output]
    ces_id <- ces_measures_combined$id[i_output]
    var_name <- ces_id # paste0('weighted_score_', ces_id)
    
    # group by city and holc ID, then compute the weighted average score for each holc ID
        ces3_redline_grouped_holc_id <- ces3_redline_intersection %>% 
            mutate(area_x_score = clipped_area * (!!as.name(ces_id))) %>% 
            group_by(redline_city, holc_id_2, holc_grade) %>% 
            summarize(total_area = sum(clipped_area), 
                      area_x_score_total = sum(area_x_score), 
                      component_poly_count = n()) %>% 
            mutate(!!var_name := area_x_score_total / total_area) %>% 
            drop_units()
        
        ces3_redline_grouped_holc_id <- ces3_redline_grouped_holc_id %>% 
            select(redline_city, holc_id_2, holc_grade, !!var_name) %>% 
            rename(city = redline_city)
    
    # add to output df
        if (i_output == 1) {
            df_output <- ces3_redline_grouped_holc_id
        } else {
            df_output <- left_join(x = df_output, 
                                   y = ces3_redline_grouped_holc_id %>% 
                                       st_drop_geometry(), 
                                   by = c('city', 'holc_id_2', 'holc_grade'))
        }
} 

df_output <- df_output %>% arrange(city, holc_grade, holc_id_2)


# write the output shapefile
    st_write(obj = df_output, 
             here('analysis-output', 
                  'redline_ces_scores',
                  paste0('redline_ces_scores', 
                                            '_', 
                                            Sys.Date(),
                                            '.shp'))
    )

```